Dismal Code: Studying the Evolution of Security Bugs

### 2013-07-10 docs/evol.tex
minor fix
with a structured abstract

\author{
% 1st. author
\alignauthor Dimitris Mitropoulos\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{dimitro@aueb.gr}
% 2nd. author
\alignauthor Vassilios Karakoidas\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{bkarak@aueb.gr}
% 3rd. author
\alignauthor Panos Louridas\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{louridas@aueb.gr}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Georgios Gousios\\
       \affaddr{Software Engineering Research Group}\\
       \affaddr{Delft University of Technology}\\
       \email{G.Gousios@tudelft.nl}
% 5th. author
\alignauthor Diomidis Spinellis\\
       \affaddr{Department of Management Science and Technology}\\
       \affaddr{Athens University of Economics and Business}\\
       \email{dds@aueb.gr}
}

\maketitle
\begin{abstract}
Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.
We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. In particular, we analyzed every project version of the repository by using a
popular static analysis tool. Then, by taking advantage of
the repository's project history and dependency data we studied
the evolution of security bugs through time. In addition, we examined
their persistence and their relationship with
a) the size of the corresponding version, and
b) other bug categories.
Our findings indicate that there is no simple rule governing the number of
security bugs as a project evolves.
In particular, we cannot say that across projects security-related
defect counts increase or decrease significantly over time.
Furthermore, security bugs are not eliminated in a
way that is particularly different from the other bugs.
In addition, the relation of security bugs with a project's size
appears to be different from the relation of the bugs
coming from other categories.
Finally, even if bugs seem to have similar behaviour,
severe security bugs seem to be unassociated with other bug categories.
\end{abstract}

@@

In this
paper we present how we used a large software ecosystem to analyse the
relationship of different types of security vulnerabilities to 
evolving software packages.
For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,HP07,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
(approximately 265GB of data---see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
This research builds upon our earlier work on the topic~\cite{MGS12}.

@@

The evolution of software artifacts has also been analysed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former, they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter, they computed a signature for every bug. This
signature contained elements like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b,KE07} proposed a history-based warning
prioritization algorithm by mining the history of bug-fixes of three
different projects. Working towards the same direction, Heckman
et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.

@@

\subsubsection{Security Bugs {\sc vs} Other Bug Categories}

>>>>

\maketitle
\begin{abstract}
{\bf Background.} Security bugs are critical programming errors that can lead to serious
vulnerabilities in software. Such bugs may allow an attacker to take over
an application, steal data or prevent the application from working at all.\\
{\bf Aim.} We used the projects stored in the Maven repository to study the
characteristics of security bugs individually and in relation to other software
bugs. Specifically, we studied
the evolution of security bugs through time. In addition, we examined
their persistence and their relationship with
a) the size of the corresponding version, and
b) other bug categories.\\
{\bf Method.} We analyzed every project version of the Maven repository by
using FindBugs, a popular static analysis tool.
To see how security bugs evolve over time we took advantage of
the repository's project history and dependency data.\\
{\bf Results.} Our results indicate that there is no simple rule governing
the number of security bugs as a project evolves.
In particular, we cannot say that across projects security-related
defect counts increase or decrease significantly over time.
Furthermore, security bugs are not eliminated in a
way that is particularly different from the other bugs.
In addition, the relation of security bugs with a project's size
appears to be different from the relation of the bugs
coming from other categories.
Finally, even if bugs seem to have similar behaviour,
severe security bugs seem to be unassociated with other bug categories.\\
{\bf Conclusions.} Our findings indicate that further research should be done
to analyze the evolution of security bugs. Given the fact that our experiment
included only Java projects, similar research could be done for another
ecosystem. Finally, the fact that projects have their own idiosyncrasies
concerning security bugs, could help us find the common characteristics
of the projects where security bugs increase over time.
\end{abstract}

@@

In this
paper we present how we used a large software ecosystem to analyse the
relationship of different types of security vulnerabilities to 
evolving software packages.
For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10,HP07,SHP06}.
Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://mvnrepository.com/}}
(approximately 265GB of data---see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
%This research builds upon our earlier work on the topic~\cite{MGS12}.

@@

The evolution of software artifacts has also been analysed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former, they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter, they computed a signature for every bug. This
signature contained elements like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b} proposed a history-based warning
prioritization algorithm by mining the history of bug-fixes of three
different projects. Working towards the same direction, Heckman
et al.~\cite{HW09,HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.

@@

\subsubsection{Security Bugs VS Other Bug Categories}
